\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Doodle Classification}

\author{\IEEEauthorblockN{Hunter Song}
\IEEEauthorblockA{
\textit{McGill ID: 260853343} \\
email address}
\and
\IEEEauthorblockN{Talha Tariq}
\textit{McGill ID: 260853343} \\
\IEEEauthorblockA{
email address}
\and
\IEEEauthorblockN{Van-Tien, Hoang}
\textit{McGill ID: 260881418} \\
\IEEEauthorblockA{
email address}
}

\maketitle

\begin{abstract}
This is the abstract
\end{abstract}

\begin{IEEEkeywords}
keywords
\end{IEEEkeywords}

\section{Introduction} 

Order of names are randomly, I agree whatever order you guys prefer and give no comments.

Briefly describe the problem and summarize your approach
and results.~\cite{akl2007dynamic}


\section{Feature Design} 
Describe and justify your pre-processing methods,
and how you designed and selected your features.
\section{ Algorithms}
 Give an overview of the learning algorithms used without
going into too much detail in the class notes (e.g. SVM derivation,
etc.), unless necessary to understand other details.
\section{Methodology}
 Include any decisions about training/validation split,
distribution choice for naive bayes, regularization strategy, any optimization
tricks, setting hyper-parameters, etc.
\section{Results}
 Present a detailed analysis of your results, including graphs
and tables as appropriate. This analysis should be broader than just
the Kaggle result: include a short comparison of the most important
hyperparameters and all 3 methods you implemented.
\section{Discussion} Discuss the pros/cons of your approach \& methodology
and suggest areas of future work.

\section{Statement of Contributions} Briefly describe the contributions of each
team member towards each of the components of the project (e.g.
defining the problem, developing the methodology, coding the solution,
performing the data analysis, writing the report, etc.) At the end
of the Statement of Contributions, add the following statement: We
hereby state that all the work presented in this report is that of the
authors.
%• References (optional).
\section{Appendix (optional)} 
Here you can include additional results, more
detail of the methods, etc.

\bibliographystyle{plain}
\bibliography{report}

\end{document}